%%
% This document was built on a template (see below) and I've made random changes
% here and there to make it as I needed.
%
% The original template was taken from:
%   http://www.LaTeXTemplates.com
% Authors:
%   - Cies Breijs (cies@kde.nl)
%   - Vel (vel@latextemplates.com)
% Original template license:
%   CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%

\documentclass[10pt,a4paper]{article}
\include{structure}
\hyphenation{}
\begin{document}

\noindent
{
    \begin{minipage}[c][][t]{0.5\textwidth}
        \maintitle{Babak Khalkhali Shandiz}
        {Software Engineer}
        {Mashhad, IRAN}
        {\href{https://github.com/babakks/my-resume}{\tiny\color{gray}\texttt{Build\buildno}}}
    \end{minipage}
    \begin{minipage}[c][][t]{0.5\textwidth}
        \small
        \raggedleft{
            \texttt{babakks}
            \href{https://github.com/babakks}{\githubmark}
            \href{https://www.linkedin.com/in/babakks/}{\linkedin}
            \href{https://dev.to/babakks}{\devbadge}
            \\
            \href{https://babakk.github.io}{\texttt{babakks.github.io}}~\emoji{computer}
            \\
            \href{skype:live:babak.k.shandiz}{\texttt{babak.k.shandiz}}~\skypeicon
            \\
            \href{mailto:babak.k.shandiz@gmail.com}{\texttt{babak.k.shandiz@gmail.com}}~\emoji{email}
            \\
        }
    \end{minipage}
}

\spacedhrule{0.1em}{-0.4em}

\roottitle{Summary} % Root section title
\vspace{-1.3em} % Reduce whitespace after the multi-column content
\begin{multicols}{2}  % Start a two-column layout
    \noindent
    I started programming at an early age. This provided me with the opportunity
    to experience some influential platforms/technologies, like
    \textit{Commodore~64} or \textit{Sinclair~Spectrum} and rather modern ones
    like \textit{VB6} or \textit{Turbo~C++}. I've been using \textit{C\#} and
    \textit{.NET} since their early days, and soon found myself being passionate
    about \textit{Object-Oriented Programming} and began exploring books and
    articles (mostly on \textit{The~Code~Project} then) on design patterns,
    application architecture, clean coding and experimenting ideas and
    self-thoughts.

    In the late 2000's, relational databases attracted my attention more than
    before. Since then, I occasionally read on database design and other
    concepts on the topic and try to make a point of following standards on my
    projects.

    Out of workplace, I actively provide consult to governmental or personal
    software projects. In my spare time, I'm a curious learner and a developer who
    is passionate about \textit{C\#}/\textit{TypeScript} and occasionally
    contributes to open-source projects. My last but not least interest is
    creating technical content based on day-to-day experience. I
    occasionally share my thoughts on my personal blog at
    \href{https://babakks.github.io}{Github} and
    \href{https://dev.to/babakks}{DEV}.

    Currently, I'm a senior software engineer at
    \href{https://cafebazaar.ir}{\emph{Cafebazaar}}, the \textit{largest}
    Iranian Android app store%
    \footnote{\label{cb-on-wiki}%
        \href{https://en.wikipedia.org/wiki/Cafe\_Bazaar}{Cafebazaar on Wikipedia}}%
    and one of the top third-party app markets world-wide%
    \footnote{\label{3rd-party-stores-on-wiki}%
        \href{https://en.wikipedia.org/wiki/List\_of\_mobile\_app\_distribution\_platforms\#Third-party\_platforms}%
        {Third-party Android app markets on Wikipedia}},
    developing high-load web services in \textit{Go} and \textit{Python}.
\end{multicols}
\spacedhrule{0.5em}{-0.4em}

\roottitle{Experiences}

\headedsection{}
{\href{https://www.cafebazaar.ir}{Cafebazaar}}
{\textsc{Mashhad, IRAN}} {
    {
            \bodytext{\textit{Cafebazaar} is the \textit{first} and \textit{largest}
                Iranian Android app market\textsuperscript{\ref{cb-on-wiki}}
                with 50M users\footnote{\label{cb-users-at-the-time}As of December 2021},
                and one of the top third-party Android app markets
                world-wide.\textsuperscript{\ref{3rd-party-stores-on-wiki}}
                As a member of the \textit{App-Delivery} team, our mission was to provide
                users with the latest versions of applications while keeping device
                compatibility as a constraint. This was achieved by heavy-load services, written in
                \textit{Go} and \textit{Python}, that served users with up to 2K~requests
                per second.
            }}

    \headedsubsection{+}
    {Senior Back-End Developer}
    {Jan '20 -- \textit{present}}
    {
        \bodytexttitle{Go, Python, Postgres, Redis, gRPC, Kubernetes}
        \bodytextitemized{\bull}{Improved update awareness (for
            externally published apps) from daily to per-hour precision (20x).}
        \bodytextitemized{\bull}{Transformed service design
            from basic thread-unsafe/single-thread to thread-safe/multi-thread.}
        \bodytextitemized{\bull}{Redesigned and re-factored
            tightly-coupled, legacy, untestable codebase into a \textit{SOLID},
            loosely-coupled, test-friendly design.}
        \bodytextitemized{\bull}{Improved service up-time
            (from unstable 95\% to stable 99.99\%) and unnecessary database
            roundtrips, by applying an LRU, Redis-backed cache.}
    }

    \headedsubsection{+}
    {R\&D + Reverse Engineering}
    {Mar '20 -- \textit{present}}
    {
        \bodytexttitle{Protobuf}
        \bodytextitemized{\bull}{Discovered undocumented
            Protobuf-based API capabilities; subject to ongoing NDA.}
    }

    \headedsubsection{+}
    {Technical Interviewer}
    {July '20 -- Dec '21}
    {
        \bodytext{As a member of the \textit{Software Enigineering Interview} team,
            I participate in review/interview process aimed at evaluation of
            applicants' coding skills. This involves evaluating various aspects
            from basics to more advanced topics including \textit{OOP} design,
            \textit{Clean Code/Architecture}, and \textit{SOLID} principles.}
        \bodytextitemized{\bull}{Developed further insight regarding people's
            coding habits and common bad practices.}
    }
}

\headedsection{}
{\href{https://www.partdp.ir}{Part Software Group}}
{\textsc{Mashhad, IRAN}} {
    {\bodytext{\textit{Part} is a \textit{Fintech} company, developing financial
                solutions in stock market related and banking fields. The
                company also aims to provide basic infrastructure services as a
                rich service cloud.}}

    \headedsubsection{+}
    {Technical Team Lead}
    {Aug '19 -- Oct '19}
    {
        \bodytexttitle{C\#, SQL~Server, ASP~.NET~MVC}
        \bodytextitemized{\bull}{Designed dynamic legal document generation tool
            in \textit{OOP} paradigm.}
    }

    \headedsubsection{+}
    {Technical Team Lead}
    {Dec '18 -- Aug '19}
    {
        \bodytexttitle{JavaScript, Redis, PM2}
        \bodytextitemized{\bull}{Reduced deployment costs via containerization
            and running with zero external setup.}
        \bodytextitemized{\bull}{Introduced detailed functional tests to make
            debugging more convenient.}
    }

    \headedsubsection{+}
    {Senior Back-End Developer}
    {Sep '18 -- Dec '18}
    {
        \bodytexttitle{JavaScript, Redis, PM2}
        \bodytext{Senior back-end developer at \textit{Public Services} team, with
            \textit{nodejs} as platform. The services include (but not limited
            to): authentication/authorization, access control, user profile,
            messaging, and file storage.}
    }
}

\headedsection{}
{\href{http:/www.krec.ir}{Khorasan Regional Electric Company (KREC)}}
{\textsc{Mashhad, IRAN}} {
    {\bodytext{KREC is a governmental company that manages and maintaines
                regional power transmission grid.}}

    \headedsubsection{+}
    {IT Consultant}
    {June '19 -- Dec '19}
    {
        \bodytext{The project is an enterprise solution that covers several aspects
            of \textit{Preventive Maintenance (PM)} routine, done on
            high-voltage substations, to remove paperworks and ultimately
            automate the current workflow. The project consists of mobile user
            interfaces, core function as back-end and relational databases.}
    }

    \headedsubsection{+}
    {Researcher \& Full-Stack Developer (Military Service for Elites)}
    {June '15 -- Aug '17}
    {
        \bodytexttitle{C\#, WPF}
        \bodytext{The research topic was to find the optimal solution for power
            transformer overloading dilemma. The implementation phase, was to
            develop a software platform that delivers research results as
            automated routines and user-friendly interfaces.}
    }

    \headedsubsection{+}
    {Researcher}
    {Nov '14 -- Sep '15}
    {
        \bodytexttitle{MATLAB}
        \bodytext{Research on \textit{REF} protection schemes in transmission
            gird.}
    }

}

\headedsection{}
{\href{http:/www.krec.ir}{Mashhad Urban Railway Operation company (MUROC)}}
{\textsc{Mashhad, IRAN}} {
    {}

    \headedsubsection{+}
    {Architect \& Developer}
    {Mar '15 -- Mar '17}
    {
        \bodytexttitle{MATLAB, \LaTeX}
        \bodytext{The project was to implement an integrated electro-mechanical
            simulation system to be used in further energy
            optimization studies. The platform was successfully realized,
            currently known as \textit{SITRAX}.}}
}

\headedsection{}
{Ferdowsi University of Mashhad (FUM)}
{\textsc{Mashhad, IRAN}}
{
    {}

    \headedsubsection{+}
    {Architect \& Full-Stack Developer}
    {March '11 -- Sep '11}
    {
        \bodytexttitle{C\#, SQL~Server, ASP~.NET~Web~Forms}
        \bodytext{Designing and implementing the \textit{National Bilateral Energy
                Market} web application using \textit{ASP~.NET} and
            \textit{SQL~Server}, as B.Sc. graduation project.}}
}

\headedsection{}
{RayanShop}
{\textsc{Mashhad, IRAN}}
{
    {\bodytext{\textit{RayanShop} was a pioneer online-shopping startup in Iran,
                long before current well-known rivals like
                \href{https://www.digikala.com}{\textit{Digikala}}.}
        }

    \headedsubsection{+}
    {Full-Stack Developer}
    {2003 -- 2004}
    {
        \bodytexttitle{ASP, VB6, Access}
        \bodytext{Developing back-end (\textit{Classic ASP}) and front-end (vanilla
            \textit{JavaScript}).}
    }
}
\spacedhrule{0.2em}{-1em}

\roottitle{OSS Contributions}

\headedsection{}
{\href{http://www.github.com/microsoft/vscode}{Microsoft VS Code (\texttt{microsoft/vscode})}}
{} {
    \headedsubsection{+}
    {Contributed}
    {}
    {\bodytext{Versions
            \href{https://github.com/microsoft/vscode-docs/blob/723adc3cdf3afca7f7cea071c03d86dc02736c2c/release-notes/v1_36.md\#thank-you}{$1.36.0$}
            and
            \href{https://github.com/microsoft/vscode-docs/blob/c52893f1c6d611e6f1f09838db922ea4453c3933/release-notes/v1_50.md\#thank-you}{$1.50.0$}.
        }}
}

\headedsection{}
{Authored VS Code Extensions}
{} {
    \headedsubsection{+}
    {\href{https://marketplace.visualstudio.com/items?itemName=babakks.vscode-vim-shortcuts}{Semi-Vim Shortcuts}
        (\href{https://github.com/babakks/vscode-vim-shortcuts}{\texttt{babakks/vscode-vim-shortcuts}})}
    {May '21}
    {
        \bodytexttitle{TypeScript}
        \bodytext{A productivity booster extension that brings VIM's navigation
            shortcuts into VS Code but without breaking editor configuration or
            interfering with the signle-mode editor style.}
    }

    \headedsubsection{+}
    {\href{https://marketplace.visualstudio.com/items?itemName=babakks.vscode-send-to-terminal}{Send to Terminal}
        (\href{https://github.com/babakks/vscode-send-to-terminal}{\texttt{babakks/vscode-send-to-terminal}})}
    {Jan '22}
    {
        \bodytexttitle{TypeScript}
        \bodytext{For shell users who need to copy some content/file from editor
            to the integrated terminal without the need to save the content in a
            separate file.}
    }
}

\headedsection{}
{Others}
{} {\bodytext{
        \href{https://github.com/microsoft/vscode-github-issue-notebooks/pulls?q=author\%3Ababakks}{VS Code Github issue notebooks},
        \href{https://github.com/ohmyzsh/ohmyzsh/pulls?q=author\%3Ababakks}{Oh My Zsh},
        \href{https://github.com/docker-library/docs/pulls?q=author\%3Ababakks}{Docker library docs},
        \href{https://github.com/helm/charts/pulls?q=author\%3Ababakks}{Helm charts}, etc.
    }}
\spacedhrule{0.2em}{-1em}

\roottitle{Education}
\headedsection{}
{Ferdowsi University of Mashhad (FUM)}
{\textsc{Mashhad, IRAN}} {
    \headedsubsection{+}
    {M.Sc. in Electric Power Engineering}
    {2011 -- 2014}
    {\bodytext{Focused on high voltage power transformer protection schemes.}}

    \headedsubsection{+}
    {B.Sc. in Electric Power Engineering}
    {2007 -- 2011}
    {\bodytext{Implemented \textit{National Bilateral Energy Market} web application
            using \textit{ASP~.NET} and \textit{SQL~Server}, as graduation project.}}
}

\headedsection{}
{Malek-e-Ashtar College-Preparatory School}
{\textsc{Mashhad, IRAN}} {
    \headedsubsection{+}
    {College-preparatory Diploma in Mathematics \& Physics Science}
    {2006 -- 2007}
    {}
}
\spacedhrule{1.6em}{-0.4em}

\roottitle{Honors \& Awards}
\headedsection{}
{Ranked 1\textsuperscript{st} among fellow students (B.Sc., GPA: $18.98/20$.)}
{2011}{}

\headedsection{}
{Ranked 1\textsuperscript{st} among fellow students (M.Sc., GPA: $19.17/20$.)}
{2014}{}

\headedsection{}
{Served military service as academic elite.}
{2015--2017}{}

\spacedhrule{0.5em}{-0.4em}


%	SKILLS SECTION

\roottitle{Skills}

\headedsection{}{Design, concepts \& protocols}{}
{\bodytext{Object oriented programming, design patterns, SOLID principles,
        loose/tight coupling concerns, dependency injection, inversion of
        control, unit/integration tests, databases, web services, SOA, REST,
        microservices.}}

\headedsection{} % Special section that has an inline header with a 'hanging' paragraph
{Implementation \& tools}
{}
{
    \bodytext{
        Here is the exhaustive set of specific languages/platforms/tools
        that I've ever worked with -- some in a daily basis, some once in while.
        So, skill levels vary depending on the subject.
    }
    \headedsubsection{+}{Programming languages}{}{\textit{C\#}, \textit{TS/JS}, \textit{Python}, \textit{Go}; Familiar with \textit{C/C++} and \textit{Java}}
    \headedsubsection{+}{Unit testing frameworks/tools}{}{\textit{NUnit}, \textit{MSTest}, \textit{Moq}, \textit{mocha}, \textit{jest}, \textit{chai}, \textit{sinon}}
    \headedsubsection{+}{Front-end technologies/tools}{}{\textit{HTML}, \textit{CSS}, \textit{jQuery}, \textit{Aurelia}, \textit{Vue.js}}
    \headedsubsection{+}{Back-end technologies/tools}{}{\textit{nodejs}, \textit{ASP~.NET MVC/Web API}, \textit{ASP~.NET Core}, \textit{express.js}, \textit{django}}
    \headedsubsection{+}{Communication methods and tools}{}{\textit{gRPC}, \textit{Protobuf}, \textit{REST}}
    \headedsubsection{+}{Databases}{}{\textit{SQL Server}, \textit{Postgres}, \textit{MongoDB}, \textit{Redis}}
    \headedsubsection{+}{Big Data Solutions}{}{\textit{Spark}, \textit{PySpark}, \textit{Hadoop}}
    \headedsubsection{+}{Messaging technologies}{}{\textit{RabbitMQ}, \textit{Kafka}}
    \headedsubsection{+}{Metering and monitoring}{}{\textit{Prometheus}, \textit{Grafana}}
    \headedsubsection{+}{Deployment automation}{}{\textit{GitLab CI}, \textit{GitHub Actions}}
    \headedsubsection{+}{Source control and interfaces}{}{\textit{GIT}, \textit{GitLab}, \textit{GitHub}}
    \headedsubsection{+}{Linux shells and tools}{}{\textit{bash}, \textit{zsh}, \textit{oh-my-zsh}}
    \headedsubsection{+}{Orchestration/Containerization and tools}{}{\textit{Kubernetes}, \textit{docker}, \textit{helm}}
    \headedsubsection{+}{IDEs, editors and development tools}{}{\textit{Visual Studio}, \textit{VS Code}, \textit{VIM}, \textit{Postman}, \textit{WebStorm}}
    \headedsubsection{+}{Miscellaneous}{}{\LaTeX, \textit{RegEx}, \textit{MATLAB}}
}


\headedsection{}
{Languages}{}
{Persian \textit{(native)}, English \textit{(full professional proficiency)}, Arabic \textit{(limited)}}


\spacedhrule{1.6em}{-0.4em}

%	INTERESTS SECTION

\roottitle{Interests}

\inlineheadsection
{Non-exhaustive and in alphabetical order:}
{
    Art,
    books,
    graphics,
    mathematics,
    music,
    open source projects,
    painting,
    problem solving,
    riddles,
    software engineering,
    studying,
    teaching,
    video games,
    writing.
}
{}

\end{document}