\documentclass[10pt,a4paper]{article}
\include{structure}
\hyphenation{}
\begin{document}

\input{title}

\section*{Statement of Purpose}

I started programming at an early age. This provided me with the opportunity
to experience some influential platforms/technologies, like
\textit{Commodore~64} or \textit{Sinclair~Spectrum} and rather modern ones
like \textit{VB6} or \textit{Turbo~C++}. I've been using \textit{C\#} and
\textit{.NET} since their early days, and soon found myself being passionate
about \textit{Object-Oriented Programming} and began exploring books and
articles (mostly on \textit{The~Code~Project} then) on design patterns,
application architecture, clean coding and experimenting ideas and
self-thoughts. Relational databases are another area of interest for me.

To summarize myself into a minium set of attributes I would say I'm a
continuos learner who hugely values technical quality. So, a job position with
lots of learning opportunities and a never-ceasing attention regard technical
qualities makes the ideal work that I could imagine. Due to this pure technical
mindset, I think, I'd be a better fit for foundational companies/projects where
their products are software platforms/systems/tools that empower other
businesses.

Out of workplace, I actively provide consult to governmental or personal
software projects. In my spare time, I'm a curious learner and a developer who
is passionate about \textit{C\#}/\textit{TypeScript} and occasionally
contributes to open-source projects. My last but not least interest is
creating technical content based on day-to-day experience. I occasionally
share my thoughts on my personal blog at
\href{https://babakks.github.io}{Github} and
\href{https://dev.to/babakks}{DEV}.

\vspace{2em}
\noindent
Sincerely \\
\noindent
Babak K. Shandiz

\end{document}
